\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{multicol}

\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%====================
% Header
%====================
\begin{center}
    {\LARGE \textbf{ANURAG SHETTIGAR}}\\
     {\textbf{Full-Stack Software Engineer}}\\
    (+91)-9082324003 |  anuragas09@gmail.com |
    Pune, India | 
    \href{https://www.linkedin.com/in/anurag-shettigar/}{LinkedIn}  | 
    \href{https://github.com/Anoteros09}{GitHub}
\end{center}

%====================
\section*{Professional Summary}

Full-stack Software Developer with \textbf{4 years and 5 months} of experience in building and modernizing applications using \textbf{React.js, Python, Julia, and AWS cloud} technologies. Proficient in designing \textbf{RESTful} services, \textbf{PostgreSQL} schema optimization, and performance tuning. Experienced in developing serverless workflows, cloud-native solutions, migrating legacy systems, building analytics dashboards, and implementing data-driven features. Strong contributor in \textbf{Agile} environments with hands-on involvement in code reviews, debugging complex issues, and end-to-end feature delivery.

%====================
\section*{Experience}

\textbf{Infosys} \hfill Pune, India \\
\textbf{Technology Analyst} \hfill Jan 2025 -- Present

\begin{itemize}[leftmargin=*]
\item Spearheaded development of Pharos, a flight schedule optimization platform.
\item Leveraged AI-powered coding assistants for debugging, refactoring, and rapid prototyping.
\item Utilized \textbf{LLM-based tools (GitHub Copilot)} for accelerated code generation.
\item Utilized AI-driven design tools for test cases, mock data, and automated code reviews.
\item Collaborated on \textbf{Micro-Frontend (MFE) architecture} using Module Federation.
\item Integrated Harness.io CI/CD pipeline to streamline deployment workflows.
\item Developed workflow orchestration using \textbf{Amazon States Language} and\textbf{ AWS Step Functions}.
\item Managed \textbf{PostgreSQL} data models with advanced versioning mechanisms.
\end{itemize}

\textbf{Infosys} \\
\textbf{Senior Systems Engineer} \hfill Jan 2024 -- Dec 2024

\begin{itemize}[leftmargin=*]
\item Led full-stack development of a resource planning application for airport operations.
\item Implemented structured code review processes, reducing bugs by 20\%.
\item Served as SME in \textbf{React.js} and \textbf{Julia}, mentoring junior developers.
\item Designed optimization features improving operational efficiency by 15\%.
\item Conducted client demos and incorporated feedback into roadmap planning.
\end{itemize}

\textbf{Infosys} \\
\textbf{Systems Engineer} \hfill Jan 2021 -- Dec 2023

\begin{itemize}[leftmargin=*]
\item Developed data-driven applications for operational cost prediction using historical data.
\item Built reusable components and enforced coding best practices.
\item Designed scalable solutions for complex business requirements.
\item Contributed actively to \textbf{Agile} ceremonies and sprint planning.
\item Led performance optimization initiatives for scalability and efficiency.
\end{itemize}

%====================
\section*{Projects}

\textbf{Schedule Development \& Optimization} \hfill Jan 2025 -- Present

\begin{itemize}[leftmargin=*]
\item Built a flight schedule optimization system using \textbf{React, Julia, and Python}.
\item Contributed to \textbf{micro-frontend architecture} and backend microservices.
\item Engineered full-stack solutions using \textbf{React.js} for frontend and \textbf{Python / Julia} for backend services.
\item Developed two \textbf{AWS}-based models using \textbf{Step Functions, Lambda, and SQS} with \textbf{Oracle DB}.
\item Designed dynamic JSON policy-based access control (IAM-style RBAC).
\item Enabled feature-level and model-level authorization governance.
\item Delivered end-to-end features independently with ownership.
\end{itemize}

\textbf{Flight Schedule Discovery} \hfill Jan 2023 -- Dec 2024

\begin{itemize}[leftmargin=*]
\item Modernized legacy Julia application to \textbf{Vue.js + Julia} stack.
\item Developed analytics dashboards comparing historical and planned schedules.
\item Delivered dynamic comparison dashboard with senior stakeholder collaboration.
\item Implemented auto-scaling metrics framework across multiple models.
\item Identified staffing inefficiencies leading to \textbf{~15\%} optimization.
\item Received VP appreciation certificate for early delivery and impact.
\end{itemize}

%====================
\section*{Education}

\textbf{SITRC} \hfill Nashik, India \\
Bachelor of Engineering \hfill Aug 2017 -- Jun 2021

%====================
\section*{Achievements}

\begin{itemize}[leftmargin=*]
\item Improved operational efficiency by \textbf{15\% }through optimization initiatives.
\item Reduced post-release bugs by \textbf{20\%} through rigorous review processes.
\item \textbf{Received client appreciation} for rapidly modernizing legacy systems.
\end{itemize}

%====================
\section*{Technical Skills}

\textbf{TechStack:} Python, Julia, React.js, Next.js, Vue.js, JavaScript \\
\textbf{Frontend:} Redux Toolkit, Micro Frontend Architechture\\
\textbf{Backend:} REST APIs, Microservices \\
\textbf{Database:} PostgreSQL, Oracle DB \\
\textbf{Cloud / DevOps:} AWS, CI/CD, Harness.io \\
\textbf{Tools:} GitHub, Copilot, Claude

%====================
\section*{Professional Responsibilities}

Technical Mentoring, Debugging Support, Code Reviews, Requirement Analysis, Cross-team Collaboration, Testing, Deployment, Feature Ownership

\end{document}